### 2020-03-30 thesis/content/chapter-ltd.tex
completed k-gnn limits section

We will now analyze what those different notions of neighborhood imply for the discriminative and computational power of 2-\acsp{gnn} in comparison to 2-\acs{wl}.
In the first step we show that the discriminative power of 2-\acsp{gnn} on all graphs $G \in \mathcal{G}$ is upper bounded by that of 1-\acs{wl} on the so-called \textit{edge neighborhood graphs} $G^{\mathcal{E}} \in \mathcal{G}^{\mathcal{E}}$.
\begin{defn}\label{defn:ltd:edge-graph}
	The \textit{edge neighborhood graph} of a given graph $G = (\mathcal{V}_G, \mathcal{E}_G)$ is defined as $G^{\mathcal{E}} \coloneqq (\mathcal{V}_{G^{\mathcal{E}}}, \mathcal{E}_{G^{\mathcal{E}}})$ with the vertices $\mathcal{V}_{G^{\mathcal{E}}} \coloneqq \{ \ldblbrace v, u \rdblbrace\, |\, (v, u) \in \mathcal{E}_G \lor v = u \}$ and the edges $\mathcal{E}_{G^{\mathcal{E}}} \coloneqq \left\{ (e, e') \in \mathcal{V}_{\mathcal{G}^{\mathcal{E}}}^2 |\, \left|e \cap e'\right| = 1 \right\}$. % chktex 21
\end{defn}
\begin{prop}\label{prop:ltd:2gnn-wl1-limit}
	The discriminative power of all 2-\acsp{gnn} $h_2$ is bounded by that of 1-\ac{wl} on edge neighborhood graphs, i.e.\ $\forall\, G, H \in \mathcal{G}: G^{\mathcal{E}} \mathrel{\simeq_1} H^{\mathcal{E}} \rightarrow h_2(G) = h_2(H)$. % chktex 21
\end{prop}
\begin{proof}
	By \cref{defn:ltd:edge-graph} it holds that $\forall e_{ij} \in \mathcal{E}_G: {\Gamma_G(v_i) \cup \Gamma_G(v_j)} = \Gamma_{G^{\mathcal{E}}}(e_{ij})$.
	Therefore the 2-\acs{gnn} convolution operation defined in \cfullref[ on ]{eq:related:kgnn-layer} can be rewritten as a vertex neighborhood convolution operator
	\begin{align*}
		Z^{(t)}[e] = \sigma\left( Z^{(t-1)}[e] W^{(t)} + \smashoperator[lr]{\sum_{e' \in \Gamma_{G^{\mathcal{E}}}(e)}} Z^{(t-1)}[e'] W_{\Gamma}^{(t)} \right)
		\text{.}
	\end{align*}
	\Cref{prop:ltd:2gnn-wl1-limit} then follows from \cref{prop:related:gcnn-wl1-limit}~(\cpageref{prop:related:gcnn-wl1-limit}).
\end{proof}
\begin{lem}\label{lem:wl1-regular-edge-neighbor-limit}
	1-\ac{wl} cannot distinguish the edge neighborhood graphs $G^{\mathcal{E}}$ and $H^{\mathcal{E}}$ of any pair of $d$-regular graphs $G$ and $H$ with $n$ vertices.
\end{lem}
\begin{proof}
	Let $G$ and $H$ be two $d$-regular graphs of size $n$.
	Their corresponding edge neighborhood graphs $G^{\mathcal{E}}$ and $H^{\mathcal{E}}$ both have $n^{\mathcal{E}} = n + \frac{nd}{2}$ vertices.
	$n$ of those edge neighborhood vertices correspond to the vertices of $G$ and $H$ respectively, we will refer to them as \textit{loop vertices} $L_G$/$L_H$.
	The remaining $\frac{nd}{2}$ edge neighborhood vertices correspond to the edges of $G$ and $H$, we will refer to them as \textit{edge vertices} $E_G$/$E_H$.

	W.l.o.g.\ we define the initial colors of the loop vertices as $\chi^{(0)}(v) = \textcolor{t_blue}{\texttt{A}}$ for all $v \in L_G \cup L_H$. % chktex 25
	The initial colors of the edge vertices are defined as $\chi^{(0)}(e) = \textcolor{t_red}{\texttt{B}}$ for all $e \in E_G \cup E_H$. % chktex 25
	Note that each loop vertex $\ldblbrace v_i, v_i \rdblbrace$ with $v_i \in \mathcal{V}_G \cup \mathcal{V}_H$ has $d$ neighbors, the edges incident to $v_i$.
	Similarly each edge vertex $\ldblbrace v_i, v_j \rdblbrace$ has $2d$ neighbors, two of which are the loop vertices $\ldblbrace v_i, v_i \rdblbrace$ and $\ldblbrace v_j, v_j \rdblbrace$ with the remaining $2d - 2$ neighbors corresponding to the edges that are incident to $e_{ij}$.

	After one color refinement step we then get $\chi^{(1)}(v) = h(\textcolor{t_blue}{\texttt{A}}, \ldblbrace \underbrace{\textcolor{t_red}{\texttt{B}}, \dots, \textcolor{t_red}{\texttt{B}}}_{d\text{ times}} \rdblbrace) \eqqcolon \textcolor{t_blue}{\texttt{C}}$ for all loop vertices $v \in  L_G \cup L_H$ and $\chi^{(1)}(e) = h(\textcolor{t_red}{\texttt{B}}, \ldblbrace \textcolor{t_blue}{\texttt{A}}, \textcolor{t_blue}{\texttt{A}}, \underbrace{\textcolor{t_red}{\texttt{B}}, \dots, \textcolor{t_red}{\texttt{B}}}_{\mathclap{2d - 2 \text{ times}}} \rdblbrace) \eqqcolon \textcolor{t_red}{\texttt{D}}$. % chktex 25
	This means that $\chi^{(0)}$ and $\chi^{(1)}$ are identical up to the color substitutions $\textcolor{t_blue}{\texttt{A}} \to \textcolor{t_blue}{\texttt{C}}$ and $\textcolor{t_red}{\texttt{B}} \to \textcolor{t_red}{\texttt{D}}$, i.e.\ $\chi^{(0)} \equiv \chi^{(1)}$, which in turn implies that 1-\ac{wl} terminates after one iteration. % chktex 25
	\Cref{lem:wl1-regular-edge-neighbor-limit} then directly follows since both $G^{\mathcal{E}}$ and $H^{\mathcal{E}}$ have $n$ vertices with the final color $\textcolor{t_blue}{\texttt{C}}$ and $\frac{nd}{2}$ vertices with the final color $\textcolor{t_red}{\texttt{D}}$, i.e.\ $G^{\mathcal{E}} \mathrel{\simeq_1} H^{\mathcal{E}}$. % chktex 25
\end{proof}
\begin{cor}
	A 2-\acs{gnn} cannot distinguish $d$-regular graphs and therefore has a lower discriminative power than 2-\ac{wl}.
\end{cor}
\begin{proof}
	The corollary directly follows from \cref{prop:ltd:2gnn-wl1-limit}, \cref{lem:wl1-regular-edge-neighbor-limit} and the fact that 2-\acs{wl} is able to distinguish most regular graphs~\cite[cor.~1.8.6]{Immerman1990}.
\end{proof}

\section{A Novel 2-\acs*{wl}-inspired \acs*{gnn}}%
\label{sec:ltd:wl2gnn}

>>>>

We will now analyze what those different notions of neighborhood imply for the discriminative and computational power of 2-\acsp{gnn} in comparison to 2-\acs{wl}.
In the first step we show that the discriminative power of 2-\acsp{gnn} on all graphs $G \in \mathcal{G}$ is upper bounded by that of 1-\acs{wl} on the so-called \textit{edge neighborhood graphs} $G^{\mathcal{E}} \in \mathcal{G}^{\mathcal{E}}$.
\begin{defn}\label{defn:ltd:edge-graph}
	The \textit{edge neighborhood graph} of a given graph $G = (\mathcal{V}_G, \mathcal{E}_G)$ is defined as $G^{\mathcal{E}} \coloneqq (\mathcal{V}_{G^{\mathcal{E}}}, \mathcal{E}_{G^{\mathcal{E}}})$ with the vertices $\mathcal{V}_{G^{\mathcal{E}}} \coloneqq \{ \ldblbrace v, u \rdblbrace\, |\, (v, u) \in \mathcal{E}_G \lor v = u \}$ and the edges $\mathcal{E}_{G^{\mathcal{E}}} \coloneqq \left\{ (e, e') \in \mathcal{V}_{\mathcal{G}^{\mathcal{E}}}^2 |\, \left|e \cap e'\right| = 1 \right\}$. % chktex 21
\end{defn}
\begin{prop}\label{prop:ltd:2gnn-wl1-limit}
	The discriminative power of all 2-\acsp{gnn} $h_2$ is bounded by that of 1-\ac{wl} on edge neighborhood graphs, i.e.\ $\forall\, G, H \in \mathcal{G}: G^{\mathcal{E}} \mathrel{\simeq_1} H^{\mathcal{E}} \rightarrow h_2(G) = h_2(H)$. % chktex 21
\end{prop}
\begin{proof}
	By \cref{defn:ltd:edge-graph} it holds that $\forall e_{ij} \in \mathcal{E}_G: {\Gamma_G(v_i) \cup \Gamma_G(v_j)} = \Gamma_{G^{\mathcal{E}}}(e_{ij})$.
	Therefore the 2-\acs{gnn} convolution operation defined in \cfullref[ on ]{eq:related:kgnn-layer} can be rewritten as a vertex neighborhood convolution operator
	\begin{align*}
		Z^{(t)}[e] = \sigma\left( Z^{(t-1)}[e] W^{(t)} + \smashoperator[lr]{\sum_{e' \in \Gamma_{G^{\mathcal{E}}}(e)}} Z^{(t-1)}[e'] W_{\Gamma}^{(t)} \right)
		\text{.}
	\end{align*}
	\Cref{prop:ltd:2gnn-wl1-limit} then follows from \cref{prop:related:gcnn-wl1-limit}~(\cpageref{prop:related:gcnn-wl1-limit}).
\end{proof}
\begin{lem}\label{lem:ltd:wl1-regular-edge-neighbor-limit}
	1-\ac{wl} cannot distinguish the edge neighborhood graphs $G^{\mathcal{E}}$ and $H^{\mathcal{E}}$ of any pair of $d$-regular graphs $G$ and $H$ with $n$ vertices.
\end{lem}
\begin{proof}
	Let $G$ and $H$ be two $d$-regular graphs of size $n$.
	Their corresponding edge neighborhood graphs $G^{\mathcal{E}}$ and $H^{\mathcal{E}}$ both have $n^{\mathcal{E}} = n + \frac{nd}{2}$ vertices.
	$n$ of those edge neighborhood vertices correspond to the vertices of $G$ and $H$ respectively, we will refer to them as \textit{loop vertices} $L_G$/$L_H$.
	The remaining $\frac{nd}{2}$ edge neighborhood vertices correspond to the edges of $G$ and $H$, we will refer to them as \textit{edge vertices} $E_G$/$E_H$.

	W.l.o.g.\ we define the initial colors of the loop vertices as $\chi^{(0)}(v) = \textcolor{t_blue}{\texttt{A}}$ for all $v \in L_G \cup L_H$. % chktex 25
	The initial colors of the edge vertices are defined as $\chi^{(0)}(e) = \textcolor{t_red}{\texttt{B}}$ for all $e \in E_G \cup E_H$. % chktex 25
	Note that each loop vertex $\ldblbrace v_i, v_i \rdblbrace$ with $v_i \in \mathcal{V}_G \cup \mathcal{V}_H$ has $d$ neighbors, the edges incident to $v_i$.
	Similarly each edge vertex $\ldblbrace v_i, v_j \rdblbrace$ has $2d$ neighbors, two of which are the loop vertices $\ldblbrace v_i, v_i \rdblbrace$ and $\ldblbrace v_j, v_j \rdblbrace$ with the remaining $2d - 2$ neighbors corresponding to the edges that are incident to $e_{ij}$.
	This is illustrated in \cref{fig:ltd:edge-neighborhood}.

	After one color refinement step we get $\chi^{(1)}(v) = h(\textcolor{t_blue}{\texttt{A}}, \ldblbrace \underbrace{\textcolor{t_red}{\texttt{B}}, \dots, \textcolor{t_red}{\texttt{B}}}_{d\text{ times}} \rdblbrace) \eqqcolon \textcolor{t_blue}{\texttt{C}}$ for all loop vertices $v \in  L_G \cup L_H$ and $\chi^{(1)}(e) = h(\textcolor{t_red}{\texttt{B}}, \ldblbrace \textcolor{t_blue}{\texttt{A}}, \textcolor{t_blue}{\texttt{A}}, \underbrace{\textcolor{t_red}{\texttt{B}}, \dots, \textcolor{t_red}{\texttt{B}}}_{\mathclap{2d - 2 \text{ times}}} \rdblbrace) \eqqcolon \textcolor{t_red}{\texttt{D}}$. % chktex 25
	This means that $\chi^{(0)}$ and $\chi^{(1)}$ are identical up to the color substitutions $\textcolor{t_blue}{\texttt{A}} \to \textcolor{t_blue}{\texttt{C}}$ and $\textcolor{t_red}{\texttt{B}} \to \textcolor{t_red}{\texttt{D}}$, i.e.\ $\chi^{(0)} \equiv \chi^{(1)}$, which in turn implies that 1-\ac{wl} terminates after one iteration. % chktex 25
	\Cref{lem:ltd:wl1-regular-edge-neighbor-limit} then directly follows since both $G^{\mathcal{E}}$ and $H^{\mathcal{E}}$ have $n$ vertices with the final color $\textcolor{t_blue}{\texttt{C}}$ and $\frac{nd}{2}$ vertices with the final color $\textcolor{t_red}{\texttt{D}}$, i.e.\ $G^{\mathcal{E}} \mathrel{\simeq_1} H^{\mathcal{E}}$. % chktex 25
\end{proof}
\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{gfx/ltd/edge-neighborhood.pdf}
	\caption{
		Illustration of the edge neighborhood graphs of two 2-regular graphs of size 6.
	}\label{fig:ltd:edge-neighborhood}
\end{figure}
\begin{prop}\label{prop:ltd:2gnn-regular-limit}
	A 2-\acs{gnn} cannot distinguish regular graphs of the same size and therefore has a lower discriminative power than 2-\ac{wl}.
\end{prop}
\begin{proof}
	The proposition directly follows from \cref{prop:ltd:2gnn-wl1-limit}, \cref{lem:ltd:wl1-regular-edge-neighbor-limit} and the fact that 2-\acs{wl} is able to distinguish most regular graphs~\cite[cor.~1.8.6]{Immerman1990}.
\end{proof}

As described in \cref{sec:related:character:wl} the discriminative power of a model is, by itself, not necessarily relevant for real-world graph datasets.
In \cfullref[ on ]{prop:related:wl2-cycle-count} we saw however that 2-\acs{wl} not only has a higher discriminative power than 1-\acs{wl} but also that it is able to count the number of $m$-cycles in a given graph for all $m \leq 7$.
This is relevant because cycle counts are a commonly used metric in real-world domains such as social network and molecular structure analysis~\cite{Milo2002}\cite{Newman2003}\cite{Welser2007}\cite{Adamson1973}\cite{Kekule1866}.
To conclude this section we now show that 2-\acsp{gnn} not only have a lower discriminative power than 2-\acs{wl} but are also unable to detect cycles.
\begin{prop}
	2-\acsp{gnn} cannot detect $m$-cycles for all $m \geq 3$.
\end{prop}
\begin{proof}
	Let $n$ be the \ac{lcm} of $3$ and some $m > 3$.
	We define $c_3 \coloneqq \frac{n}{3}$ and $c_m \coloneqq \frac{n}{m}$.
	Based on that we define the following two graphs:
	Let $G_3$ be a graph consisting of $c_3$ disconnected cycles of length $3$, analogously let $G_m$ be a graph consisting of $c_m$ disconnected cycles of length $m$.
	Since both $G_3$ and $G_m$ are 2-regular and have the size $n$, any 2-\ac{gnn} $h_2: \mathcal{G} \to \mathcal{Y}$ must map both of them to the same $y \in \mathcal{Y}$ by \cref{prop:ltd:2gnn-regular-limit}.

	Let us assume that $h_2$ is able to detect cycles of length $3$, i.e.\ triangles.
	By \cfullref[ on ]{defn:related:wl-count-detect} this would imply that there is a function $g: \mathcal{Y} \to \{ 0, 1\}$ s.t.\ $g(h_2(G_3)) = g(y) = 1$ and $g(h_2(G_m)) = g(y) = 0\ \lightning$.
	Conversely, assuming that $h_2$ is able to detect cycles of length $m > 3$, we obtain the contradiction $g(h_2(G_3)) = g(y) = 0$  and $g(h_2(G_m)) = g(y) = 1\ \lightning$.
	This concludes the proof.
\end{proof}

In this section we compared 2-\acsp{gnn} with the 2-\acs{wl} algorithm and found that they have a significantly lower discriminative and computational power than 2-\acs{wl}.
Motivated by those limitations we describe a novel graph convolution operator which is closer to 2-\acs{wl} in the following section.

\section{A Novel 2-\acs*{wl} Inspired \acs*{gnn}}%
\label{sec:ltd:wl2gnn}

### 2020-03-30 thesis/content/chapter-related-work.tex
completed k-gnn limits section

For $k = 1$ \citet{Babai1980} have shown that two randomly selected non-isomorphic graphs $G \not\simeq H$ of size $n$ are 1-\acs{wl} indistinguishable with probability $n^{-\nicefrac{1}{7}}$.
Thus 1-\acs{wl} is already able to distinguish most graphs; it fails however to distinguish any pair of unlabeled $d$-regular graphs of the same size~\cite[cor.~1.8.5]{Immerman1990}.
\begin{defn}
	A graph $G$ is called \textit{$d$-regular} ($\mathit{rg}_d(G)$) iff.\ $\forall v \in \mathcal{V}_G: {|\Gamma_G(v)|} = d$.
\end{defn}
We have already seen this in \cref{fig:related:wl1-problem} since the ``six-cycle'' and the ``two-triangles'' graphs are in fact both 2-regular and of size 6.
This restriction alone is typically not an issue in the context of \ac{gcr} though, as molecular structures or social interaction graphs for example are rarely perfectly regular.
A more relevant restriction of 1-\acs{wl} is the fact that it is unable to detect cycles of length $m \geq 3$.
\begin{defn}\label{defn:related:wl-compute}
	$k$-\acs{wl} \textit{computes} a function $f: \mathcal{G} \to Y$ iff.\ that function can be expressed as $f(G) = g(\mathit{dist}_{\chi_{G, k}^{*}})$ via some function $g: (\mathcal{C} \to \mathbb{N}) \to Y$.
\end{defn}
\begin{defn}\label{defn:related:wl-count-detect}
	$k$-\acs{wl} \textit{counts} a certain ordered subgraph $S \in \mathcal{G}_{\mathit{ord}}$ iff.\ it computes $\mathit{count}_S(G) \coloneqq \left|\{ \set(v)\, |\, v \in \mathcal{V}_G^{*} \land G[v] \equiv S \}\right|$ (see~\cref{defn:related:ordered-subgraph}).
	Similarly $k$-\acs{wl} \textit{detects} an ordered subgraph $S$ iff.\ it computes $\mathit{contain}_S(G) \coloneqq \mathbbm{1}[\mathit{count}_S(G) > 0]$, with $\mathbbm{1}$ denoting the indicator function.
\end{defn}
To see why 1-\acs{wl} is unable to detect $m$-cycles in graphs, note that \cref{fig:related:wl1-problem} already contradicts the positive statement for $m = 3$;
this counterexample can be trivially generalized to all larger $m$ by replacing the ``six-cycle'' graph with a ``$(2m)$-cycle-graph'' graph and the ``two-triangles'' graph with a ``two-$m$-cycles'' graph which preserves the 2-regularity and therefore the 1-\acs{wl} indistinguishability.

@@

If we increase the \acs{wl}-dimension to $k = 2$, the described 1-\acs{wl} restrictions no longer apply.
2-\acs{wl} is able to distinguish more than $1 - \mathcal{O}(\nicefrac{1}{n})$ of the regular $n$-vertex graphs~\cite[cor.~1.8.6]{Immerman1990} and can even count cycles:
\begin{prop}[see \citet{Fuerer2017} and \citet{Arvind2019} for the full proof]\label{prop:related:wl2-cycle-count}
	2-\acs{wl} is able to count $m$-cycles for $m \leq 7$ but it cannot detect 8-cycles.
\end{prop}
\begin{hproof}
	Only the idea behind triangle and 4-cycle counting is outlined here to give an intuition for why \cref{prop:related:wl2-cycle-count} holds.
	Note that the 2-\acs{wl} neighbors of each edge $(v, w) \in \mathcal{E}_G$ correspond to all possible paths $(v, u, w)$ of length 2, i.e.\ all possible triangles.
	By \cref{defn:related:wlk-refine} there must thus be a color subset $C^{\triangle}_j \subseteq \mathcal{C}$ representing that an edge is involved in exactly $j$ triangles after one refinement step.
	2-\acs{wl} then trivially counts triangles by setting $g(\mathit{dist}_\chi) = \frac{1}{3} \sum_j j \sum_{c \in C^{\triangle}_j} \mathit{dist}_\chi(c)$ to satisfy \cref{defn:related:wl-compute}.
	Analogously for 4-cycles, let $C^{\square}_j \subseteq \mathcal{C}$ be the colors indicating a non-edge $(v, w) \notin \mathcal{E}_G$ with $j$ common vertex neighbors $u \in \Gamma_G(v) \cap \Gamma_G(w)$.
	The number of 4-cycles is then determined by the colors of the diagonals through them via $g(\mathit{dist}_\chi) = \frac{1}{2} \sum_{j \geq 2} \binom{j}{2} \sum_{c \in C^{\square}_j} \mathit{dist}_\chi(c)$.
	Using a similar but more involved combinatorial argument requiring multiple color refinement steps, 5-, 6- \& 7-cycle counting can be shown.
\end{hproof}
As we just saw, 2-\acs{wl} is significantly more powerful than 1-\acs{wl}.
Though, by \cref{prop:related:wl-upper}, there are of course still 2-\acs{wl} indistinguishable graphs;
among others those are the strongly regular graphs $\mathit{srg}_{n, d, \lambda, \mu}(G)$.
\begin{defn}
	$\begin{aligned}[t]
		\mathit{srg}_{n, d, \lambda, \mu}(G) \iff\ & {|\mathcal{V}_G|} = n \quad\land\quad \forall v \in \mathcal{V}_G: {|\Gamma_G(v)|} = d \\
		&\land \forall (v, w) \in \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \lambda \\
		&\land \forall (v, w) \in \mathcal{V}_G^2 \setminus \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \mu
	\end{aligned}$
\end{defn}
Generally this restriction of 2-\acs{wl} is not an issue since strongly regular graphs do not appear in typical \ac{gcr} datasets.
By going to $k = 3$, even some strongly regular graphs as well as all planar graphs can be distinguished though~\cite{Kiefer2017}.
Apart from that there are currently few results regarding the classes of distinguishable graphs and computable functions for even higher \ac{wl}-dimensions.

>>>>

For $k = 1$ \citet{Babai1980} have shown that two randomly selected non-isomorphic graphs $G \not\simeq H$ of size $n$ are 1-\acs{wl} indistinguishable with probability $n^{-\nicefrac{1}{7}}$.
Thus 1-\acs{wl} is already able to distinguish most graphs; it fails however to distinguish any pair of unlabeled $d$-regular graphs of the same size~\cite[cor.~1.8.5]{Immerman1990}.
\begin{defn}
	A graph $G$ is called \textit{$d$-regular} ($\mathit{rg}_d(G)$) iff.\ $\forall v \in \mathcal{V}_G: {|\Gamma_G(v)|} = d$.
\end{defn}
We have already seen this in \cref{fig:related:wl1-problem} since the ``six-cycle'' and the ``two-triangles'' graphs are in fact both 2-regular and of size 6.
This restriction alone is typically not an issue in the context of \ac{gcr} though, as graphs in many real-world domains are rarely perfectly regular~\cite{Abedijaberi2018}.
A more relevant restriction of 1-\acs{wl} is the fact that it is unable to detect cycles of length $m \geq 3$.
\begin{defn}\label{defn:related:wl-compute}
	$k$-\acs{wl} \textit{computes} a function $f: \mathcal{G} \to Y$ iff.\ that function can be expressed as $f(G) = g(\mathit{dist}_{\chi_{G, k}^{*}})$ via some function $g: (\mathcal{C} \to \mathbb{N}) \to Y$.
\end{defn}
\begin{defn}\label{defn:related:wl-count-detect}
	$k$-\acs{wl} \textit{counts} a certain ordered subgraph $S \in \mathcal{G}_{\mathit{ord}}$ iff.\ it computes $\mathit{count}_S(G) \coloneqq \left|\{ \set(v)\, |\, v \in \mathcal{V}_G^{*} \land G[v] \equiv S \}\right|$ (see~\cref{defn:related:ordered-subgraph}).
	Similarly $k$-\acs{wl} \textit{detects} an ordered subgraph $S$ iff.\ it computes $\mathit{contain}_S(G) \coloneqq \mathbbm{1}[\mathit{count}_S(G) > 0]$, with $\mathbbm{1}$ denoting the indicator function.
\end{defn}
To see why 1-\acs{wl} is unable to detect $m$-cycles in graphs, note that \cref{fig:related:wl1-problem} already contradicts the positive statement for $m = 3$;
this counterexample can be trivially generalized to all larger $m$ by replacing the ``six-cycle'' graph with a ``$(2m)$-cycle-graph'' graph and the ``two-triangles'' graph with a ``two-$m$-cycles'' graph which preserves the 2-regularity and therefore the 1-\acs{wl} indistinguishability.

@@

If we increase the \acs{wl}-dimension to $k = 2$, the described 1-\acs{wl} restrictions no longer apply.
2-\acs{wl} is able to distinguish more than $1 - \mathcal{O}(\nicefrac{1}{n})$ of the regular $n$-vertex graphs~\cite[cor.~1.8.6]{Immerman1990} and can even count cycles:
\begin{prop}[see \citet{Fuerer2017} and \citet{Arvind2019} for the full proof]\label{prop:related:wl2-cycle-count}
	2-\acs{wl} is able to count $m$-cycles for all $m \leq 7$ but it cannot even detect them for $m > 7$.
\end{prop}
\begin{hproof}
	Only the idea behind triangle and 4-cycle counting is outlined here to give an intuition for why \cref{prop:related:wl2-cycle-count} holds.
	Note that the 2-\acs{wl} neighbors of each edge $(v, w) \in \mathcal{E}_G$ correspond to all possible paths $(v, u, w)$ of length 2, i.e.\ all possible triangles.
	By \cref{defn:related:wlk-refine} there must thus be a color subset $C^{\triangle}_j \subseteq \mathcal{C}$ representing that an edge is involved in exactly $j$ triangles after one refinement step.
	2-\acs{wl} then trivially counts triangles by setting $g(\mathit{dist}_\chi) = \frac{1}{3} \sum_j j \sum_{c \in C^{\triangle}_j} \mathit{dist}_\chi(c)$ to satisfy \cref{defn:related:wl-compute}.
	Analogously for 4-cycles, let $C^{\square}_j \subseteq \mathcal{C}$ be the colors indicating a non-edge $(v, w) \notin \mathcal{E}_G$ with $j$ common vertex neighbors $u \in \Gamma_G(v) \cap \Gamma_G(w)$.
	The number of 4-cycles is then determined by the colors of the diagonals through them via $g(\mathit{dist}_\chi) = \frac{1}{2} \sum_{j \geq 2} \binom{j}{2} \sum_{c \in C^{\square}_j} \mathit{dist}_\chi(c)$.
	Using a similar but more involved combinatorial argument requiring multiple color refinement steps, 5-, 6- \& 7-cycle counting can be shown.
\end{hproof}
As we just saw, 2-\acs{wl} is significantly more powerful than 1-\acs{wl}.
Though, by \cref{prop:related:wl-upper}, there are of course still 2-\acs{wl} indistinguishable graphs;
among others those are the strongly regular graphs $\mathit{srg}_{n, d, \lambda, \mu}(G)$.
\begin{defn}
	$\begin{aligned}[t]
		\mathit{srg}_{n, d, \lambda, \mu}(G) \iff\ & {|\mathcal{V}_G|} = n \quad\land\quad \forall v \in \mathcal{V}_G: {|\Gamma_G(v)|} = d \\
		&\land \forall (v, w) \in \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \lambda \\
		&\land \forall (v, w) \in \mathcal{V}_G^2 \setminus \mathcal{E}_G: {|\Gamma_G(v) \cap \Gamma_G(w)|} = \mu
	\end{aligned}$
\end{defn}
Generally this restriction of 2-\acs{wl} is not an issue since strongly regular graphs do not appear in typical \ac{gcr} datasets.
By going to $k = 3$, even some strongly regular graphs as well as all planar graphs can be distinguished though~\cite{Kiefer2017}.
Apart from that there are currently few results regarding the classes of distinguishable graphs and computable functions for even higher \ac{wl}-dimensions.
